### 2011-05-12 paper.tex
Added conclusion

>>>>

The results from this paper show that the view of complexity of promise problems, or alternatively the complexity of partial functions, leads to results of similar interest to those that result from the study of languages. Additionally, partial functions offer very natural definitions for operators, especially randomized operators, on complexity classes. Our work does suggest several directions for futuer work.
Some of these might include developing similar groundwork for different contexts, such as operators for quantum complexity classes, function classes, or for classes that are smaller than $\p$ or larger than $\textsf{PSPACE}$. Additionally, it could be interesting to consider other operators in this context, such as $\mod k$ for general $k$, and their relationships to the ones we define here.
